---
title: "Airquality Assignment"
author: "Sulchan Yoon"
date: "`r Sys.Date()`"
format: html
editor: visual
---

## Startup

Tidyverse to process and handle most plots. rbokeh to process plot 5. Setting wd to where all class files are.

```{r}
library(tidyverse)
library(rbokeh)
setwd("~/Data Study/Data110 MC/Week 1")

airquality <- airquality
```

\newpage

## EDA - Exploratory Data Analysis

The first few aspects are a copy of the sample description for this project. The later portion speaks on N/A handling. After confirmation, none of the p1-p4 plots use data within the N/A cols.

```{r}
# Summary and general statistics
mean(airquality$Temp)
mean(airquality[,4])
median(airquality$Temp)
sd(airquality$Wind)
var(airquality$Wind)

#summary of data structure
str(airquality)
head(airquality)

# Relabel and re-review
airquality$Month[airquality$Month == 5]<- "May"
airquality$Month[airquality$Month == 6]<- "June"
airquality$Month[airquality$Month == 7]<- "July"
airquality$Month[airquality$Month == 8]<- "August"
airquality$Month[airquality$Month == 9]<- "September"
#review summary of data structure
str(airquality)
head(airquality)

#re-review summary statistics
summary(airquality)

#order the months
airquality$Month<-factor(airquality$Month, levels=c("May", "June","July", "August", "September"))
```

\newpage

## Data Wrangling

```{r}
# check for N/A
na.cols <- which(colSums(is.na(airquality)) >0)
sort(colSums(sapply(airquality[na.cols], is.na)),decreasing = TRUE)

paste('Number of columns with no values:', length(na.cols))

which(is.na(airquality), arr.ind=TRUE)
# What can we do with these N/A? Is it necessary for analysis?
```

\newpage

## Graphics

```{r}
p1 <- qplot(data = airquality,Temp,color = Month,geom = "histogram", bins = 20)
p1

p2 <- airquality %>%
  ggplot(aes(x=Temp, fill=Month)) +
  geom_histogram(position="identity", alpha=0.5, binwidth = 5, color = "black")+
  scale_fill_discrete(name = "Month", labels = c("May", "June","July", "August", "September"))
p2

p3 <- airquality %>%
  ggplot(aes(Month, Temp, fill = Month)) + 
  ggtitle("Temperatures") +
  xlab("Monthly Temperatures") +
  ylab("Frequency") +
  geom_boxplot() +
  scale_fill_discrete(name = "Month", labels = c("May", "June","July", "August", "September"))
p3 

p4 <- airquality %>%
  ggplot(aes(Month, Temp, fill = Month)) + 
  ggtitle("Monthly Temperature Variations") +
  xlab("Monthly Temperatures") +
  ylab("Frequency") +
  geom_boxplot()+
  scale_fill_grey(name = "Month", labels = c("May", "June","July", "August", "September"))
p4
```

\newpage

## Challenge Myself with Different Plots

```{r}
## Plot 5 - My own plot

#test of color ramp
#n <- nrow(airquality)
#ramp <- colorRampPalette(c("green","blue","yellow"))(n)
p5 <- figure() %>%
  ly_points(Temp, Wind, data = airquality, color = Month, glyph = Month)
p5

#recreate the same rbokeh graph into a ggplot
p6 <- airquality %>%
  ggplot(aes(Temp, Wind, shape = Month, color = Month, alpha = 0.5)) +
  geom_point(size = 4) + 
  scale_shape_manual(values=c(16,15,17,18,10))+
  scale_color_manual(values=c('blue','orange','green','red','purple'))
p6
```

\newpage

## Discussion on my Graph

"Be sure to write a brief essay that describes the plot you have created, what the plot shows, and what code you used to make this modification."
